Argennon: A Scalable Smart Contract Platform

### 2021-07-11 tex/sections/avm.tex
Make the AVM RESTful
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon\footnote{the classical pronunciation should be used:\textipa{/Ar"gen.non/}} Virtual Machine (AVM) is an
abstract computing machine for executing Argennon's smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, only of Argennon's identifier tries and
the concept of execution sessions.

Execution sessions are separate sessions of executing smart contact's code by the Argennon Virtual Machine.
These sessions are usually correspondent to the concept of a transaction in a blockchain. (See
Section~\ref{sec:execution-sessions})

@@

Every AVM execution session has a queue of call stacks. A call stack contains all the information that is needed for
restoring the state, and continuing the execution after the method invocation completes.
This information is represented by a \texttt{CallInfo} struct:
\begin{verbatim}
CallInfo {
    applicationID,
    methodID,
    pc,
    canModify,
    localFrame,
    operandStack
}
\end{verbatim}
The \texttt{applicationID} field is the unique identifier that the AVM assigns to every smart contract,
\texttt{methodID} is the unique identifier of a method's bytecode and \texttt{canModify} is a flag
indicating whether a method is allowed to execute state modifying instructions or not.

Every method invocation has a corresponding \texttt{CallInfo} struct and when a method is invoked its
\texttt{CallInfo} struct is pushed onto the call stack. Hence, the top of the call stack always contains
the \texttt{CallInfo} struct of the current method. When a method invocation completes its call
information is popped from the call stack.

An AVM execution session will continue as long as there is a non-empty call stack in the call stack queue. When the
execution of the current call stack finishes the execution of the next call stack in the call stack queue starts.
It's possible that an AVM method invocation creates new call stacks. These newly created call stacks will be a part
of the current execution session and are added at the end of the call stack queue. A newly created call stack always
contains a single \texttt{CallInfo} struct. See Section~\ref{subsec:method-invocation} for more details.

@@

Instructions that modify the code area can only be run in privileged mode which means they can only be executed
by the \emph{root} smart contract. As a result, the access of smart contracts to the code area is essentially
read-only.

@@

Every smart contract has a single constant area which is stored in the AVM code area as a special type of
non-executable method. The constant area of a smart contract contains several kinds of constants, ranging from user
defined constants to method address tables. A method address table stores the list of methods of a smart
contract and their access type. The access type of method can be either \texttt{external} or \texttt{internal}.
Only external methods can be invoked by \texttt{invoke\_external} instruction.

@@

A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
those chunks that was created by itself. In other words, every memory chunk in the AVM heap has an owner. Only
the owner can modify a chunk while anyone can read that chunk. In addition, for modifying a chunk the \texttt{canModify}
flag of the current method's \texttt{callInfo} struct must be true. The owner of a chunk can be easily determined
by the \texttt{applicationID} part of the chunk identifier.

\note{The reason behind this type of access control design is the fact that smart contract code is usually
immutable. That means if a smart contract does not implement a getter mechanism for some parts of its internal
data, this functionality can never be added later. Although the internal data is publicly available, there will
be no way for other smart contracts to use this data on-chain. This design eliminates the need for implementing
\emph{trivial} getters.}

@@

The Argennon Virtual Machine has four types of method invocation instruction:
\begin{itemize}
    \item \texttt{invoke\_internal}: invokes a method without changing the context of method execution. In other
    words, \texttt{applicationID} and \texttt{canModify} fields of the invoked method in the
    call stack will be the same as the invoker.
    A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
    internal method of another smart contract. Since the invoked method will always be executed in the context of
    the invoking smart contract, a smart contract will not be able to modify another smart contract state by
    this instruction. This instruction facilitates code reuse and the usage of libraries.
    \item \texttt{invoke\_external}: invokes a method and changes the context of method execution to another
    smart contract. Only external methods of another smart contract can be called by this instruction. For changing
    the context of method execution this instruction sets the \texttt{applicationID} field of the invoked method
    to the \texttt{applicationID} of the called smart contract. Then it searches the call stack and if
    the \texttt{applicationID} of the called smart contract is found in the current call stack it sets
    \texttt{canModify} to \texttt{false}, otherwise \texttt{canModify} is set to \texttt{true}.
    As a result, if the called smart contract is already called, the invoked method will not be
    able to modify the heap area.
    \item \texttt{invoke\_native}: invokes a method that is not hosted by the Argennon Virtual Machine. By this
    instruction, high performance native methods of the hosting machine could become available to AVM smart
    contracts. This instruction will not modify the AVM state.
    \item \texttt{spawn}: spawns a new method invocation. Spawning a method invocation is the invocation of a method
    with changing the context of method execution and creating a new call stack. Only external methods can
    be spawned. The created call stack is added at the end of the call stack queue and
    the \texttt{canModify} field of the pushed \texttt{CallInfo} struct will always
    be set to \texttt{true}. This instruction does not modify the \texttt{pc} register and the execution of the
    caller will continue after this instruction. As a result, \texttt{spawn} can not return
    any value to the caller and the return value of the called method (if any) will be added
    to the transaction output. If the invoked method completes abruptly, it will cause all the call stack queue to
    complete abruptly.
\end{itemize}

@@

Each time a method is invoked the \texttt{Save()} function of the AVM heap is called, then a new local frame
and operand stack is created. The Argennon Virtual Machine uses local frames to pass parameters on
method invocation. On method invocation, any parameters are passed in consecutive local variables stored in the
method's local frame starting from address 0. The invoker of a method writes the parameters in the local frame
of the invoked method using \texttt{arg} instructions.

\note{For AVM smart contracts \emph{reentrancy} can only happen in read-only mode and is totally safe.
At the same time, call-back patterns can be easily implemented by using \texttt{spawn} instruction.}

@@

An exception is thrown programmatically using the \texttt{athrow} instruction. Exceptions can also be thrown by
various Argennon Virtual Machine instructions if they detect an abnormal condition. Some exceptions are not
catchable and will always abort the method invocation.

\note{By using the \texttt{athrow} instruction properly, a programmer can make any method act like an atomic
operation.}

@@

A method invocation completes normally if that invocation does not cause an exception to be thrown, either
directly from the AVM or as a result of executing an explicit throw statement. If the invocation of the current
method completes normally and the invocation was made by an \texttt{invoke} instruction, then a value may be
returned to the invoking method. This occurs when the invoked method executes one of the return instructions, the
choice of which must be appropriate for the type of the value being returned (if any). Execution then continues
normally in the invoking method's local frame with the returned
value (if any) pushed onto the operand stack. If the method was invoked by a \texttt{spawn} instruction,
the execution of the next call stack (if any) begins and the returned value
is appended at the end of the transaction output. When a method invocation completes normally,
the \texttt{Heap.Discard()} function is called as a part of the return instruction.

A method invocation completes abruptly if an exception is thrown and is not caught by the current method. A
method invocation that completes abruptly never returns a value.

When a method completes, whether normally or abruptly, the call stack is used to restore the state of the invoker,
including its local frame and operand stack, with the \texttt{pc} register appropriately restored and incremented
to skip past the method invocation instruction. If the current call stack is empty the next call stack in the call
stack queue will be used for continuing the execution, and when there are no call stacks left in the queue the
current execution session ends.

A thrown exception causes methods in the call stack to complete \emph{abruptly} one by one, as long as the
\texttt{pc} register is not pointing to a \texttt{catch} instruction. The \texttt{catch} instruction acts like a
branch instruction that branches only if an exception is caught. When an exception is thrown
Algorithm~\ref{alg:Abrupt} is used to restore the state of the AVM heap.

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Heap}{Heap}\SetKwData{Stack}{CallStack}
    \SetKwFunction{Discard}{Discard}\SetKwFunction{Pop}{pop}\SetKwFunction{Restore}{Restore}
    \SetKwProg{Fn}{Function}{}{}

    \While{\Stack is not empty}
    {
        \Stack.\Pop{}\;
        \eIf{\Stack is not empty \textbf{and} $\Stack[head].pc \rightarrow catch$}
        {
            \Heap.\Restore{}\;
        }{
            \Heap.\Discard{}\;
        }
    }
    \Heap.\Restore{}\;
    \caption{Abrupt method completion}\label{alg:Abrupt}
\end{algorithm}

A closer investigation of Algorithm~\ref{alg:Abrupt} shows that when an invocation which was made by
a \texttt{spawn} instruction completes abruptly, the heap snapshot that was saved before the start of the
execution of the first call stack of the execution session is restored. Since the root
smart contract calls \texttt{Heap.Save()} function before spawning the requested method, this means
that all changes made to the AVM heap during the execution session will be restored, but the changes made by
the root smart contract including the transferring of the transaction fee will not be restored. See
Section~\ref{sec:execution-sessions} for more details.

@@

\section{Execution Sessions}\label{sec:execution-sessions}

The execution of smart contracts code by the Argennon Virtual Machine is performed in execution sessions. Every
execution session consists of a single method invocation from the \emph{root} smart contract and a list
of resource allocation requests. These allocation requests always include a request for allocating some amount
of execution cost and a request for accessing some memory locations for reading or writing. If after starting,
an execution session tries to violate its allocated resources, an \textbf{uncatchable} exception will
be thrown by the AVM\@.

\note{The AVM does not have a \texttt{calldata} memory area. The arguments of the root smart contract method will
be copied from the transaction to the local frame of the invoked method, exactly like a normal method invocation.}

The root smart contract with the \texttt{applicationID} of zero, is a special smart contract in the Argennon
Virtual Machine. Its code is mutable and is a part of the Argennon protocol. The root smart contract is always
run in the privileged mode, and every Argennon transaction starts with a call to a method of the root smart contract.
This method always transfers some amount of fee from an account to the \texttt{feeSink} accounts and then it
performs the requested operation.

If the requested operation is a method invocation, the root smart contract will call the \texttt{Heap.Save()}
function, and then it will invoke the requested method using \texttt{spawn} instruction. This implies that the
invoked method will always have a separate call stack, and if it completes abruptly the changes made by the root
smart contract to the AVM state will not be reverted.

\note{Argennon transactions do not have a sender, and the payer of the transaction fee could be any
account who has provided the required digital signature for the fee payment.}

>>>>

The Argennon\footnote{the classical pronunciation should be used:\textipa{/Ar"gen.non/}} Virtual Machine (AVM) is an
abstract computing machine for executing Argennon's smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, transactions or any concept of gas usage, only of
Argennon's identifier tries and the concept of execution sessions.

Execution sessions are separate sessions of executing smart contract's code by the Argennon Virtual Machine.
Every execution session starts with a single method invocation, but does not necessarily end when
that method invocation completes. During an execution session additional method invocations could be scheduled,
which will be executed after the initial method completion.

An execution session may complete normally or abruptly. When an execution session completes abruptly, it will
not have any effects on the AVM state.

@@

Every AVM execution session has a queue of call stacks. A call stack contains all the information that is needed for
restoring the AVM state, and continuing the execution after the method invocation completes.
This information is represented by a \texttt{CallInfo} struct:
\begin{verbatim}
CallInfo {
    methodID,
    pc,
    localFrame,
    operandStack
}.
\end{verbatim}

The \texttt{methodID} field is the unique identifier of a method's bytecode that
is a composite prefix code built by concatenating an \texttt{applicationID} to
a local identifier.

Every method invocation has a corresponding \texttt{CallInfo} struct and when a method is invoked its
\texttt{CallInfo} struct is pushed onto the call stack. Hence, the top of the call stack always contains
the \texttt{CallInfo} struct of the current method. When a method invocation completes, its call
information is popped from the call stack.

An AVM execution session will continue as long as there is a non-empty call stack in the call stack queue. When the
execution of the current call stack finishes, the execution of the next call stack in the call stack queue starts.
It is possible that an AVM method invocation creates new call stacks. These newly created call stacks will be a part
of the current execution session and are added at the end of the call stack queue. A newly created call stack always
contains a single \texttt{CallInfo} struct. See Section~\ref{subsec:method-invocation} for more details.

@@

Every smart contract is required to have a special \texttt{dispatcher} method. The \texttt{dispatcher} method is the
only method of a smart contract that can be called by other smart contracts and has a
predefined \texttt{methodID}: \texttt{(ApplicationID|0)}.

\note{The Argennon Virtual Machine does not have internal or external methods. All methods are considered internal
except the \texttt{dispatcher} method, which is the only external method of any smart contract.
This design enables the AVM to execute smart contracts with \emph{RESTful} APIs more efficiently.}

Instructions that modify the code area can only be run in privileged mode, which means they can only be executed
by the \emph{root} smart contract. As a result, the access of smart contracts to the code area is essentially
read-only.

@@

Every smart contract has a single constant area which is stored in the AVM code area as a special type of
non-executable method. The constant area of a smart contract contains user
defined constants.

@@

A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
those chunks that was created by itself. In other words, every memory chunk in the AVM heap has an owner. Only
the owner can modify a chunk while anyone can read that chunk. The owner of a chunk can be easily determined
by the \texttt{applicationID} part of the chunk identifier.

\note{The reason behind this type of access control design is the fact that smart contract code is usually
immutable. That means if a smart contract does not implement a getter mechanism for some parts of its internal
data, this functionality can never be added later, and despite the internal data is publicly available, there will
be no way for other smart contracts to use this data on-chain. This design eliminates the need for implementing
\emph{trivial} getters.}

@@

The Argennon Virtual Machine has four types of method invocation instruction:
\begin{itemize}
    \item \texttt{invoke\_internal}: invokes a method without changing the context of method execution. In other
    words, the invoked method can only modify the state of the current smart contract.
    A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
    internal method of another smart contract. Since the invoked method will always be executed in the context of
    the invoking smart contract, a smart contract will not be able to modify another smart contract state by
    this instruction. This instruction facilitates code reuse and the usage of libraries.
    If the invoked method completes abruptly, that will cause the invoker method to complete abruptly too.
    \item \texttt{invoke\_dispatcher}: invokes the \texttt{dispatcher} method of a smart contract and changes the
    context of method execution to that
    smart contract. If the invoked method completes abruptly, that will cause the invoker method to complete
    abruptly too.
    \item \texttt{i\_invoke\_dispatcher, i\_invoke\_internal}: independently invokes a method. These instructions
    are similar to their \texttt{invoke} counterparts, with the difference that when
    the invoked method completes abruptly, the invoker method can continue execution. When a method invoked by
    an \texttt{i\_invoke} instruction completes abruptly, all changes made
    by the invoked method to the AVM state will be reverted and the instruction will act like
    a jump to the specified error handling code.
    \item \texttt{invoke\_native}: invokes a method that is not hosted by the Argennon Virtual Machine. By this
    instruction, high performance native methods of the hosting machine, such as GPU accelerated operations,
    could become available to AVM smart contracts. This instruction will not modify the AVM state.
    \item \texttt{invoke\_later}: invokes the \texttt{dispatcher} method of another smart contract by creating a new
    call stack. The created call stack is added at the end of the call stack queue, and
    the context of method execution will change after the execution of that call stack starts. This instruction does
    not modify the \texttt{pc} register and the execution of the
    invoker will continue after this instruction. As a result, \texttt{invoke\_later} can not return
    any values to the caller and the return value of the called method (if any) will be discarded. If the invoked
    method completes abruptly, it will cause \textbf{all the call stack queue to
    complete abruptly.}
\end{itemize}

\note{The \texttt{invoke\_later} instruction can be used to call a smart contract while its reentracy lock is active.
Because the invocation uses a separate call stack, it will not cause the lock to throw an exception.}

Each time a method is invoked a new local frame
and operand stack is created. If the method was invoked by an \texttt{i\_invoke} instruction,
the \texttt{Save()} function of the AVM heap is called before the execution of the method starts.

The Argennon Virtual Machine uses local frames to pass parameters on
method invocation. On method invocation, any parameters are passed in consecutive local variables stored in the
method's local frame starting from address 0. The invoker of a method writes the parameters in the local frame
of the invoked method using \texttt{arg} instructions.

@@

@@

An exception is thrown programmatically using the \texttt{athrow} instruction. Exceptions can also be thrown by
various Argennon Virtual Machine instructions if they detect an abnormal condition.

\note{Any AVM instruction may throw an exception. This happens when the execution cost of a transaction has exceeded
the declared execution cost of the transaction.}

@@

A method invocation completes normally if that invocation does not cause an exception to be thrown, either
directly from the AVM or as a result of executing an explicit throw statement. If the invocation of the current
method completes normally and the invocation was not made by an \texttt{invoke\_later} instruction, then a value may be
returned to the invoking method. This occurs when the invoked method executes one of the return instructions, the
choice of which must be appropriate for the type of the value being returned (if any). Execution then continues
normally in the invoking method's local frame with the returned
value (if any) pushed onto the operand stack. If the method was invoked by an \texttt{invoke\_later} instruction,
the execution of the next call stack (if any) begins and the returned value
is discarded. When a method invocation that was made by
an \texttt{i\_invoke} instruction completes normally,
the \texttt{Heap.Discard()} function is called as a part of the return instruction.

A method invocation completes abruptly when an exception is thrown by one its instructions.
The \texttt{invoke\_internal} and \texttt{invoke\_dispatcher} instructions
always throw an exception when their invoked method completes abruptly. A
method invocation that completes abruptly never returns a value.

When a method completes normally, the call stack is used to restore the state of the invoker,
including its local frame and operand stack, with the \texttt{pc} register appropriately restored and incremented
to skip past the method invocation instruction. If the current call stack is empty the next call stack in the call
stack queue will be used for continuing the execution, and when there are no call stacks left in the queue the
current execution session ends.

When a method completes abruptly, the call stack is used to restore the \texttt{pc} register of the invoker. If the pc
register points to an \texttt{invoke} instruction, the current method completes abruptly as well. Otherwise, if
the \texttt{pc} register is pointing to an \texttt{i\_invoke} instruction, the \texttt{Heap.Restore()} function is
called to restore the state of the AVM heap. Then, the
local frame and operand stack of the invoker is restored, and execution continues after branching to the error handling
code specified by the instruction operand.

When an invocation which was made by an \texttt{invoke\_later} instruction completes abruptly, the
heap snapshot that was saved before the start of the
execution of the first call stack is restored. This means
that all changes made by the execution session to the AVM heap will be completely reverted.

\subsection{Reentrancy Protection}\label{subsec:reentrancy}

The Argennon Virtual Machine provides low level reentrancy protection by defining a dedicated
instruction: \texttt{enter}. When a smart contract executes the \texttt{enter} instruction, it
can not execute that instruction again as long
as the method executing that instruction completes (abruptly or normally). If a smart contract tries to execute
the \texttt{enter} instruction, while the method executing that instruction for the first time has not yet completed,
an exception will be thrown.

Smart contracts can completely prevent reentrancy by executing \texttt{enter} instruction as the first instruction
of their \texttt{dispatcher} method.

@@

### 2021-07-11 tex/sections/draft.tex
Make the AVM RESTful
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

>>>>

If the pc register points to an \texttt{invoke} instruction, the current method completes abruptly too.
including its local frame and operand stack, with the \texttt{pc} register appropriately restored and incremented
to skip past the method invocation instruction. If the current call stack is empty the next call stack in the call
stack queue will be used for continuing the execution, and when there are no call stacks left in the queue the
current execution session ends.

When an exception is thrown
Algorithm~\ref{alg:Abrupt} is used to restore the state of the AVM heap.

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Heap}{Heap}\SetKwData{Stack}{CallStack}
    \SetKwFunction{Discard}{Discard}\SetKwFunction{Pop}{pop}\SetKwFunction{Restore}{Restore}
    \SetKwProg{Fn}{Function}{}{}

    \While{\Stack is not empty}
    {
        \Stack.\Pop{}\;
        \eIf{\Stack is not empty \textbf{and} $\Stack[head].pc \rightarrow catch$}
        {
            \Heap.\Restore{}\;
        }{
            \Heap.\Discard{}\;
        }
    }
    \Heap.\Restore{}\;
    \caption{Abrupt method completion}\label{alg:Abrupt}
\end{algorithm}

A closer investigation of Algorithm~\ref{alg:Abrupt} shows that when an invocation which was made by
a \texttt{spawn} instruction completes abruptly, the heap snapshot that was saved before the start of the
execution of the first call stack of the execution session is restored. Since the root
smart contract calls \texttt{Heap.Save()} function before spawning the requested method, this means
that all changes made to the AVM heap during the execution session will be restored, but the changes made by
the root smart contract including the transferring of the transaction fee will not be restored. See
Section~\ref{sec:execution-sessions} for more details.

### 2021-07-11 tex/sections/elements.tex
Make the AVM RESTful
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Argennon has two special smart contracts: the \emph{root} smart contract\footnote{also called the root app} and
the \emph{ARG} smart contract\footnote{also called the Argennon smart contract or the Argennon app.}.
The root smart contract, with \texttt{applicationID=[0x0]}, is a privileged smart contract responsible for
method invocation and installation/uninstallation of other smart contracts.
On the other hand, the ARG smart contract, with \texttt{applicationID=[0x1]}, controls the ARG token, the main
currency of the Argennon blockchain, and also manages a database of public keys and handles signature verification.

Both of these smart contracts are mutable smart contracts and can be updated by the Argennon governance protocol.

@@

Every Argennon transaction is a single \texttt{invoke\_external} instruction which calls a method from the Argennon
root smart contract. This method always transfers the proposed fee of the transaction in ARGs from a
sender account to the fee sink accounts and then performs the requested operation. The Argennon root smart contract
has four public methods:

\begin{itemize}
    \item \texttt{avmCall}: invokes a method from an
    AVM smart contract. Users interact with AVM smart contracts using this method of the root smart contract.
    Transferring all assets, including ARG, is done by these transactions.
    \item \texttt{installApp}: installs an AVM smart contract and determines the update policy of the smart
    contract: if the contract is updatable or not, which accounts can update or uninstall the contract, and so
    on.
    \item \texttt{unInstallApp}: removes an AVM smart contract.
    \item \texttt{updateApp}: updates an AVM smart contract (if allowed).
\end{itemize}

@@

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. The protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs, and every transaction is required
to specify a maximum execution cost. If during emulation, a transaction reaches this maximum cost, it will be
considered failed and the network can receive the proposed fee of that transaction.

@@

\begin{itemize}
    \item Maximum execution cost
    \item A list of heap/code-area locations for reading
    \item A list of heap locations for writing
    \item A list of heap chunks it will deallocate
    \item A list of methods it will delete (if any)
    \item Number and size of heap chunks it will allocate
    \item Number and size of method bytecodes it will allocate (if any)
\end{itemize}

@@

Every Argennon transaction is required to pay two types of fees: execution fee and storage fee. A transaction pays
its fees by providing digital signatures of one or more accounts, authorizing the transfer of the amount of fee in
ARG from one or more accounts to the fee sink accounts.

>>>>

Argennon has two special smart contracts: the \emph{root smart contract}, also called the \emph{root application}, and
the \emph{ARG smart contract}, which is also called the Argennon smart contract or the \emph{ARG application}.

\subsection{The Root Application}\label{subsec:the-root-app}

The root application or the root smart contract, with \texttt{applicationID=[0x0]}, is a privileged smart contract
responsible for installation/uninstallation of other smart contracts. The Argennon root smart contract
performs three main operations:

\begin{itemize}
    \item Installation of AVM smart contracts and determining the update policy of a smart
    contract: if the contract is updatable or not, which accounts can update or uninstall the contract, and so
    on.
    \item Removing AVM smart contracts.
    \item Updating an AVM smart contract (if allowed).
\end{itemize}

The root smart contract is a mutable smart contract and can be updated by the Argennon governance system.
(See Section~\ref{sec:adags})

\subsection{The ARG Application}\label{subsec:the-arg-app}

The ARG application or the ARG smart contract,
with \texttt{applicationID=[0x1]}, controls the ARG token, the main
currency of the Argennon blockchain. This smart contract also manages a database of public keys and
handles signature verification.

The ARG smart contract is a mutable smart contract and can be updated by the Argennon governance system.

@@

Every Argennon transaction consists of two \texttt{i\_invoke\_dispatcher} instructions, the first instruction always
transfers the proposed fee of the transaction in ARG from a sender account to the fee sink accounts, and
the second performs the requested operation.

Users interact with AVM smart contracts using
the second \texttt{i\_invoke\_dispatcher} instruction of a transaction,
Transferring all assets, including ARG, is done by that instruction.

@@

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. When a transaction reaches one of its
pre-declared resource caps, executing any AVM instruction which uses that resource, will result in an AVM exception.

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. As a result, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.} and the remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum costs, executing any instruction which has
that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still keep executing
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker fail unconditionally
by using infinite loops.}

@@

\begin{itemize}
    \item Maximum internal execution cost
    \item Maximum external execution cost
    \item A list of heap/code-area locations for reading
    \item A list of heap locations for writing
    \item A list of heap chunks it will deallocate
    \item A list of methods it will delete (if any)
    \item Number and size of heap chunks it will allocate
    \item Number and size of method bytecodes it will allocate (if any)
\end{itemize}

@@

Every Argennon transaction is required to pay two types of fees: execution fee, which is paid for executing the
transaction, and storage fee, which is paid for the amount of storage the transaction allocates.

A transaction pays
its fees by providing digital signatures of one or more accounts, authorizing the transfer of the amount of fee in
ARG from one or more accounts to the fee sink accounts, and the fee is transferred by the first
\texttt{i\_invoke\_dispatcher} instruction of the transaction.
